---
title: "oop_vCtrl_prjMgt"
author: "LB"
date: "February 28, 2019"
output: html_document
---

```{r vCtrl, include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

## Version Control
Version control is a crucial consideration, espectially when working with collaborators. We will try and collaborate on this project so, we will learn how to set up git on your machine and integrated into RStudio. Jenny Bryan also has a wonderful book online that provides an in-depth step-by-step on how to truly get git working smoothly, check it out here <https://happygitwithr.com>. 
  Overview:  

1. Register a [GitHub](https://github.com) account
2. Install Windows: [Git](https://git-scm.com/) / macOS: Xcode
3. Get your GitHub known to RStudio
```{r git}
library(usethis)
use_git_config(user.name = "labouz", user.email = "lab218@miami.edu")
```
4. Install a Git [client](https://sourcetreeapp.com) (*optional*)
5. Make a test repo on GitHub.com
6. Connect RStudio to Git and GitHub
7. Create project with verison control

### What is Git?

### What is a Git client?

### Create a test repo and connect to RStudio


## Object-Oriented Programming (OOP)

## Project Management

RStudio makes it easy organize and manage your project. Built-in functions, like "New Project" or "Import Data" aim to make your life a little easier. Let's start with creating a self-contained, reproducible project. It's a good idea to create a new project before starting a new script - that way, all data and code within that project can be easily picked back up after a break.

 How to create a project:

1. Click "File", "New Project"
2. Click "New Directory"
3. Click "New Project"
4. Name your project


